---
title: "Thank you, Jupiter Broadcasting!"
format: PrettyPDF-pdf
---

```{r}
#| label: setup
#| include: false

library(qrcode)
```

```{=html}
<style>
.flushright {
   text-align: right;
}
</style>
```


Hello, Chris!

I know you've heard me say this before, but I am so thankful for Jupiter Broadcasting opening my eyes to the exciting possibilities of how far we can take open-source software and how Linux would eventually bring immense value to both my career and my podcasting / Linux adventures at home. And if that wasn't enough, I also have you to thank for discovering value for value and Podcasting 2.0. This Atari VCS was begging for a new home, and I dare say you and the JB crew are going to have a load of fun with it!

One small bit of history: While I had little time to play with the console itself, the gamepad included in this package was a huge part of my online Hotshot Racing adventures with Martin Wimpress and a merry band of racing enthusiasts. The QR code below takes you to my favorite racing session!

```{r}
#| label: racingcode
#| echo: false
#| fig-width: 2.0
#| fig-height: 2.0

plot(qr_code("https://www.youtube.com/watch?v=ow8A68ElPp0"))
```

Speaking of open-source, this letter was written with a completely open-source stack:

* OS: KDE Neon 22.04
* Editor: RStudio IDE[^1]
* Publishing Engine: Quarto[^2]
* Computing Language: R[^3] (of course)

[^1]: <https://posit.co>
[^2]: <https://quarto.org>
[^3]: <https://r-project.org>

::: {.flushright data-latex=""}
Sincerely,

Eric Nantz (R-Podcast)

<https://podcastindex.social/@rpodcast>
:::

